\documentclass[a4paper]{arthur-letter}

\title{Fascist presence in California hotels ignites Ex Navy SEAL Matt Woods.}

\author{Matthew Woods F.K.A. Burns}

\usepackage[english]{babel}
\usepackage{fontspec}
\usepackage{luatexbase}
\usepackage{microtype}

% only needed for the example
\usepackage{lipsum}

%%=================%%
%%  Custom colors  %%
%%=================%%

% \definecolor{boxcolor}{HTML}{0E5484}
% \definecolor{maincolor}{HTML}{1a4c70}
% \definecolor{secondcolor}{HTML}{4d4d4d}

%%==========%%
%%  Header  %%
%%==========%%

% Set profile info [Following information are optional]
\letname{Matthew Woods F.K.A. Burns}            % Your full name
\linkedin{matthew-woods-f-k-a-burns-2b90491b8}       % Your linkedin
\mail{mattwoods243@outlook.com}       % Your email
\numberphone{+1 808 300 8426}                % Your phone number
\lettitle{Fascist hotel conglomerates (e.g. Marriot Group, Inc.) team up with police to assault, rob and intimidate Ex Navy SEAL Matthew Woods F.K.A. Burns in California} % Title of your letter
\site{mattwoods5326.wixsite.com/xignalxincformerlyxi}                       % Your site
\github{matthewwoods243}

\profilepic{}

\begin{document}
    \makeprofile % Set header
    
    % English commands (address and location at right and recipient at left)
    \address{Matthew Woods,\\PO Box 376\\Mountain View, CA, 94042}

    \begin{letter}

    \subject{TLDR: I'm a former Navy SEAL, smeared by Dianna Cowern (AKA Physics Girl) via Alphabet Inc. while working as a Google employee. From 2015-2020, I have experienced severe police misconduct first hand. This is across five counties: San Diego, Orange, Santa Clara, Oahu and Hawaii. I think they may have ties to THE Nazis, since my entire immediate family (Donald Burns, Anne Burns and Susan Burns) are Nazis... the type that agree with Adolf Hitler and Eichmann of WWII. They lied to me about this since I was born. Target Corporation, local strip malls and police succumb to fascism and try to suppress me in all ways. on top of that, Citigroup Inc. and Wells Fargo launch denial of service attacks to me and XignalX Inc: a struggling startup owned by disabled former US Navy SEALs in Hawaii. Nation state level hacking is apparent. Police, employers, hotel conglomerates and former Navy team mates cooperate to rob, assault and lie to me in concert.
}
            
    \opening{Dear New York Times,}
    
    This installment details the mistreatment and abuse suffered foremost at the hands of the California police. More alarming than that was the reality that they were not operating alone: my roommates, employers and doctors were colluding with the Nazis (yes, from WWII). An example that has happened at least 20 times, no exaggeration: My hotel stay, fully booked gets disrupted by fascist hotel staff who tell lies about me and cooperate with the police in those lies. Sometimes they go as far as assaulting me. I had a shakedown at Cape Rey, Carlsbad, to that effect. I had just quit Google and was stopping down in San Diego for a few days. The police pounced on me in a gas station parking lot and separated me from my vehicle (Audi Q5 2018). They had some kind of warrant from 2017, that I vaguely remember the incident. This is right around when Owens died and got a Medal of Honor. I had been living in Mountain View for well over a year since then. This is an old ticket. Turned out to be a misdemeanor. What I experienced was being thrown in jail. This begs the question: who called the cops on me while sitting in my car at a gas station. They claimed some ''anonymous'' person called them, which we know isn't true. This was my first time in jail, a Nazi setup of some kind. Apparently they track me somehow, including the Audi. 
    
    I have proof of this happening again months later in conjunction with some bad actor ex teammates, who are veteran Navy SEALs. They were doing something with local law enforcement, which is similar to Garett McDermid AKA "Roomba". All three of them, Lopez, Munoz and McDermid, are acquaintances from the SEALs, but I did not work with any of them. McDermid likes to lie and say we worked at SEAL team five together. We did not. We went to a month long class called NSW Communications, and that is it. We mountain biked together after I left the Navy, and I even went to his wedding. The Audi may have been hacked to get my position in 2019, but in 2020, the gas gauge was hacked. The gauge went from 60 miles to zero miles instantaneously. I got off the freeway because of this, but had trouble from local police about finding a parking spot for a fuel vehicle to come. I drove that vehicle another six hours, making my way across town to Santa Clara. The drama continued from there, but I ditched that Audi in the street because of the gas gauge hack. It was surely not trustworthy. 
    
    In the frequentist approach to statistics, you can calculate the probability of an event happening by the number of times it already happened (i.e. the percentage of occurrence of some event overall). Since I quit Google in 2019, the probability that the police will cooperate with any hotel I choose randomly is high. With over 20 instances overall, the probability of being harassed by the hotel and the police at the same time FOR NO REASON is in the high 90's. ''I'd say it's a soft 90 sir'', if you want to be all "Zero Dark Thirty" about it. I say this of random hotels in CA, which is alarming. Since I was dealing with hotels professionally in the late 2000s in the military, Marriott Group, Inc. has subsumed many of the hotel brands that I preferred, such as Starwood. I believe they have also succumbed to Fascism. There are other incidents which are slightly varied, such as the W San Francisco trying such maneuvers on me, sans police. I was escorted out of the hotel by some "manager" known as Keith for no reason, and they wouldn't answer my demands to know why. Now I know; it was a fascist Nazi conspiracy in the San Francisco Bay area, but the cops didn't play into it, making it not quite an instance (I call the variable ''thecopsandthehotel'', but as I mentioned you can make it more general by including strip malls, restaurants, etc). I'm here to tell everyone, it's not me, it's them. Many Marriott hotels are included, especially the Aloft Santa Clara which I had a court case about. What occurs is massive scale LYING about me in the computer systems on both the hotel and the police side. As I mentioned, I have over 20 occurrences of this event ''thecopsandthehotel'' with maybe four counterexamples which would equate to a good hotel stay with no serious dings. Since 2019, normal hotel stays have been out of the question, which I can claim having worked with them at a high level before. What changed? Hitler POTUS Trump is a new feature, maybe it has something to do with him.
    
    U-Haul Group, Inc. and Expedia Group, Inc. have horror stories attached to them which might be more widespread in the number of people they affect. From the Mountain View (i.e. Google) U-Haul, I rented a 26' truck and collected all of my belongings to flee the bay area under persecution from the local police, employers and random people on the street. The truck was not serviceable, blowing up the front tire twice on the freeway. It was as if they had some environment set up for me in CA, but my leaving the area would incapacitate their effort. Rather than submit to their ''environment'', I chose to ditch the U-Haul where they brought it in Oakland, CA and change my destination to Hawaii instead of Lake Tahoe. This is due entirely to U-Haul not honoring their service obligations. My belongings are in their hands to this day, to the tune of \$60K in property. After being marooned in Oakland by U-Haul, I attempted to stay at a bed and breakfast titled "Dream Catcher" from expedia.com. I encountered a hostile environment, where my property was stolen by the host, as well as physical agression. I called expedia.com over fifteen times to lodge a formal complaint about the host. They would not write the complaint down in their system, instead choosing to lie to me 15 times that they had done so and would address it. They suggested a few times that I call the police if I have a complaint, which is a complete lack of responsibility on their end. This is right before I came to Hawaii. It seems like nothing works for me all at once, which is a conspiracy with many bad actors, presumably from the Nazis. I think there could be millions of them based on my samples from the field, such as these.
    
            
    \cite{targetcorporationhitlersalute} \cite{bigbangtheoryhouse5058pendleton} \cite{stripmalls} \cite{deptofva} \cite{googlenaziexpose} .
    
    
            
            \closing{Yours sincerely,} % To adapt following recipient

            \signing{Matthew Woods (F.K.A. Burns)}

    \end{letter}
    
\begin{thebibliography}{}

\bibitem{alphabetinc}
Alphabet, Inc, https://documentcloud.adobe.com/link/review?uri=urn:aaid:scds:US:8016c2b0-e71f-4c2c-995d-b67174459387

\bibitem{targetcorporationhitlersalute}
Target Corporation, https://documentcloud.adobe.com/link/review?uri=urn:aaid:scds:US:f7522e8c-d944-449d-8fbd-f68dd59e60cb

\bibitem{bigbangtheoryhouse5058pendleton}
Big Bang Theory House (ft The Physics Girl), http://courtindex.sdcourt.ca.gov/CISPublic/casedetail?casenum= DV041758\&casesite=SD\&applcode=D

\bibitem{stripmalls}
Strip Malls, https://documentcloud.adobe.com/link/review?uri=urn:aaid:scds:US:83be49a8-3869-4166-9204-21ff644ca4ac

\bibitem{deptofva}
Department of Veterans Affairs, https://documentcloud.adobe.com/link/review?uri=urn:aaid:scds:US:d3408823-1435-45c6-85ce-014178982796

\bibitem{googlenaziexpose}
Google, Inc, https://documentcloud.adobe.com/link/review?uri=urn:aaid:scds:US:59b02f2f-74cd-4123-826b-5afd40aa18d4

\end{thebibliography}
\end{document}
